---
title: "Journal Rankings"
author: "Patrick"
format: html
server: shiny
---

## Shiny Documents

This Quarto document is made interactive using Shiny. Interactive documents allow readers to modify parameters and see the results immediately. Learn more about Shiny interactive documents at <https://quarto.org/docs/interactive/shiny/>.

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change. This demonstrates how a standard R plot can be made interactive:

```{r}
selectizeInput(inputId = "journal", 
            label = "Select a Journal:",
            choices = NULL)
plotOutput("rankPlot")
```

```{r}
#| message: false
#| warning: false
#| context: server

library(tidyverse)

jif <- read_tsv("sociology_politicalscience.csv") |> 
    group_by(source) |> 
    mutate(dist = abs(pctile_journal - quantile(pctile_journal, probs = .5)))

updateSelectizeInput(session, 'journal', 
                       choices = sort(unique(jif$source)), 
                       server = TRUE)

output$rankPlot <- renderPlot({
  x <- jif |> 
    filter(source == input$journal)
  
  median_pctile_class <- min(x$pctile_class[x$dist == min(x$dist)])
  min_pctile_class <- min(x$pctile_class)
  min_pctile_journal <- min(x$pctile_journal)
  
  x <- x |> 
    group_by(pctile_class) |> 
    slice_max(pctile_journal)
  
  ggplot(x, aes(x = pctile_class,
                  y = pctile_journal)) +
    geom_point(col = "darkblue") +
    geom_step(col = "darkblue") +
    geom_abline(slope = 1, intercept = 0, lty = 2) +
    theme_minimal() +
    geom_segment(x = 0, xend = median_pctile_class,
                 y = 50, yend = 50,
                 lty = 3, col = "darkgreen") +
    geom_segment(x = median_pctile_class, 
                 xend = median_pctile_class,
                 y = 0, yend = 50,
                 lty = 3, col = "darkgreen") +
    geom_segment(x = 0, xend = min_pctile_class,
                 y = min_pctile_journal, yend = min_pctile_journal,
                 lty = 3, col = "darkred") +
    geom_segment(x = min_pctile_class, 
                 xend = min_pctile_class,
                 y = 0, yend = min_pctile_journal,
                 lty = 3, col = "darkred") +
    labs(title = input$journal,
         y = "Journal Percentile",
         x = "Category Percentile")
})
```